Practical Hilbert space approximate Bayesian Gaussian processes for probabilistic programming

### 2022-02-16 Paper/Manuscript_Stats&Comp/manuscript_STCO.tex
more edits

\begin{itemize}
\item As $\ell$ increases, $m$ required for an accurate approximation decrease.
\item The lower $c$, the smaller $m$ can and $\ell$ must be to achieve an accurate approximation.
\item For a given $\ell$ there exist a minimum $c$ under which a accurate approximation is never going to be achieved regardless of $m$. This fact can be seen in Figures~\ref{fig6_7_relationships} and \ref{fig6_7_relationships} as the contour lines which represent $c$ have an end in function of $\ell$ (Valid $c$ are restricted in function of $\ell$). As $\ell$ increases, the minimum valid $c$ also increases.
\end{itemize}

@@

Having obtained an estimate $\hat{\ell}$ of $\ell$ from the HSGP model based on prespecified $m$ and $c$, we can check whether or not $\hat{\ell}$ exceeds the minimum length-scale provided in Figure~\ref{fig6_7_relationships} (depending on which kernel is used). If $\hat{\ell}$ exceeds this recommended minimum length-scale, the approximation is assumed to be good. If, however, $\hat{\ell}$ does not exceed recommended minimum length-scale, the approximation may be inaccurate and $m$ should be increased or $c$ decreased. We may also use this diagnostic in an iterative procedure by starting from some initial guess of $\ell$ and initial values for $m$ and $c$, and if the estimated $\hat{\ell}$ is below the minimum length-scale, repeat the process while increasing $m$ or decreasing $c$. As mentioned earlier, $c$ cannot be decreased too much as the lowest useful value of $c$ is restricted by the length-scale. Thus, increasing $m$ may usually the preferred approach.

If we look back to the conclusions drawn from Figures~\ref{fig4_MSE_vs_J} and \ref{fig5_lscale_vs_J}, where $m = 10$ basis functions and a boundary factor of $c = 1.5$ were sufficient to obtain an accurate approximation of a function with $\ell = 0.3$, we can recognize that these conclusions also matches those obtained from Figure~\ref{fig6_7_relationships}.

@@

@@

\begin{enumerate}
\item[Step A1.] Make an initial guess on true the lengthscale $l_1$ of the function to be learned. We recommend a large lengthscale, about $l_1 \approx 1$. Set the iteration index to $i=1$.
%\item[] \hspace{-1cm} \textit{(Initial iteration, $i=1$)}
\item[Step A2.] Obtain the minimum valid boundary factor $c_i$ determined by $l = l_i$ for the given kernel as per Section \ref{num_equations} 
\item[Step A3.] Obtain the mimimum valid number of basis functions $m_i$ determined by $l = l_i$ and $c = c_i$ for the given kernel as per Section \ref{num_equations}. 
\item[Step A4.] Fit an HSGP model using $m_i$ and $c_i$ and ensure convergence of the MCMC chains.
\item[Step A5.] Perform the lengthscale diagnostic by checking if $\hat{l}_i \pm 0.02 \geq l_i$.

>>>>

\begin{itemize}
\item As $\ell$ increases, $m$ required for an accurate approximation decrease.
\item The lower $c$, the smaller $m$ can and $\ell$ must be to achieve an accurate approximation.
\item For a given $\ell$ there exist a minimum $c$ under which a accurate approximation is never going to be achieved regardless of $m$. This fact can be seen in Figures~\ref{fig6_7_relationships} and \ref{fig6_7_relationships}
% TODO FIX the figure reference!
as the contour lines which represent $c$ have an end in function of $\ell$ (Valid $c$ are restricted in function of $\ell$). As $\ell$ increases, the minimum valid $c$ also increases.
\end{itemize}

@@

Having obtained an estimate $\hat{\ell}$ of $\ell$ from the HSGP model based on prespecified $m$ and $c$, we can check whether or not $\hat{\ell}$ exceeds the minimum length-scale provided in Figure~\ref{fig6_7_relationships} (depending on which kernel is used). If $\hat{\ell}$ exceeds this recommended minimum length-scale, the approximation is assumed to be good. If, however, $\hat{\ell}$ does not exceed recommended minimum length-scale, the approximation may be inaccurate and $m$ should be increased or $c$ decreased. We may also use this diagnostic in an iterative procedure by starting from some initial guess of $\ell$ and initial values for $m$ and $c$, and if the estimated $\hat{\ell}$ is below the minimum length-scale, repeat the process while increasing $m$ or decreasing $c$. As mentioned earlier, $c$ cannot be decreased too much as the lowest useful value of $c$ is restricted by the length-scale. Thus, increasing $m$ is usually the preferred approach.

If we look back to the conclusions drawn from Figures~\ref{fig4_MSE_vs_J} and \ref{fig5_lscale_vs_J}, where $m = 10$ basis functions and a boundary factor of $c = 1.5$ were sufficient to obtain an accurate approximation of a function with $\ell = 0.3$, we can recognize that these conclusions also match those obtained from Figure~\ref{fig6_7_relationships}.

@@

If the initial lengthscale is not far from the optimal, and larger than minimal $c$ and $m$ are used in the first fitting, it is likely that the result is sufficiently accurate. The following iterative approach works as safety approach and allows also finding a smaller sufficient $m$ which can be useful if the user wants to optimized the computational speed for repeated fitting (e.g. in cross-validation or simulation based calibration).

@@

\begin{enumerate}
\item[Step A1.] Make an initial guess on the lengthscale $l_1$. If there is no useful information available, we recommend to start with a large lengthscale, about $l_1 \approx 1$. Set the iteration index to $i=1$.
%\item[] \hspace{-1cm} \textit{(Initial iteration, $i=1$)}
\item[Step A2.] Obtain the minimum valid boundary factor $c_i$ determined by $l = l_i$ for the given kernel as per Section \ref{num_equations} .
\item[Step A3.] Obtain the mimimum valid number of basis functions $m_i$ determined by $l = l_i$ and $c = c_i$ for the given kernel as per Section \ref{num_equations}. 
\item[Step A4.] Fit an HSGP model using $m_i$ and $c_i$ and ensure convergence of the MCMC chains.
\item[Step A5.] Perform the lengthscale diagnostic by checking if $\hat{l}_i \pm 0.02 \geq l_i$.
